Verifying Demonstrations

### 2019-02-20 paper/protocol.tex
Fixes Syntastic warnings

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}
\label{Protocol}

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares they have signed, \eg by giving a list 
of all such proof shares or digitally signing each proof share\footnote{
 To achieve witness privacy in this situation, one could employ a group or 
 ring signature scheme for all trusted witnesses.
 Then one learns that at least one trusted witness must have been there.
}.

>>>>

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}%
\label{Protocol}

@@

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares they have signed, \eg by giving a list of all 
such proof shares or digitally signing each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a group or 
  ring signature scheme for all trusted witnesses.
  Then one learns that at least one trusted witness must have been there.
}.

### 2019-02-20 paper/verifiability-analysis.tex
Fixes Syntastic warnings

The strength function from ~\cref{DefParticipationCount} ensures that
Alice either has to collude with \(\theta - 1\) witnesses (she can
produce \emph{one} witness signature for herself, since she has access
to her own \(\sk_P\), but no more) or, in the trusted witness case,
that Alice must be able to forge statements, \eg digital signatures,
from at least one witness that the verifier trusts.

>>>>

The strength function from \cref{DefParticipationCount} ensures that
Alice either has to collude with \(\theta - 1\) witnesses (she can
produce \emph{one} witness signature for herself, since she has access
to her own \(\sk_P\), but no more) or, in the trusted witness case,
that Alice must be able to forge statements, \eg digital signatures,
from at least one witness that the verifier trusts.
